---
title: "Nadav report"
output:
  html_document: default
  pdf_document: default
  word_document: default
editor_options:
  chunk_output_type: console
  always_allow_html: TRUE
  numbersections: true
  header-includes:
   - "\\usepackage{float}"
   - "\\usepackage{graphicx}"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$get('label')
```


```{r read data}
setwd("C:/Users/ido/sheba stats/nadav")
library("lubridate")
library("tidyr")
library("dplyr")
library("labelled")
library("tableone")
library("knitr")
library("kableExtra")
library("gt")
library("gtsummary")
library("janitor")
library("ggplot2")
library("plotrix")
library("circlize")
library("readxl")
```

\tableofcontents
\clearpage 

# Norton 18
```{r norton}
before = read_excel('נורטון 18 לפני ירידה למרתף.xlsx', sheet='Norton')
before = before[-(1:6),]
after = read_excel('נורטון 18 אחרי חזרה מהמרתף.xlsx', sheet='Norton')
after = after[-(1:6),]

before$Norton = as.integer(before[['...7']])
after$Norton = as.integer(after[['...7']])

combined <- data.frame(Before = before$Norton, After = after$Norton)
```

### Before
```{r}
summary(before$Norton)

```
### after
```{r}
summary(after$Norton)

```
### P value is larger than 0.05, groups are **not** statistically different

```{r}

# 4. Statistical Tests
# Example: t-test for a continuous variable 'variable_of_interest'
t_test_result <- t.test(before$Norton, after$Norton)
print(t_test_result)
```


```{r}
# Scatter plot
plot(combined$Before, combined$After, xlab = "Before", ylab = "After", main = "Scatter plot of Norton values Before and After")
abline(0, 1, col = "red")  # Add a diagonal line for comparison

# Box plot
boxplot(combined, col = c("blue", "green"), names = c("Before", "After"), main = "Box plot of Before and After", xlab = "Group")

# Bar plot
mean_before <- mean(combined$Before)
mean_after <- mean(combined$After)
sd_before <- sd(combined$Before)
sd_after <- sd(combined$After)

# Create bar plot
means <- c(mean_before, mean_after)
stds <- c(sd_before, sd_after)
barplot(means, names.arg = c("Before", "After"), ylab = "Measurement", main = "Bar plot of Norton Means with Std Deviations", col = "blue", ylim = c(0, max(means) + max(stds) + 5))
arrows(x0 = c(0.7, 1.9), y0 = means - stds, y1 = means + stds, angle = 90, code = 3, length = 0.1)

```

# Norton 18א
```{r norton A}
before = read_excel('נורטון 18א לפני ירידה למרתף.xlsx', sheet='Norton')
before = before[-(1:6),]
after = read_excel('נורטון 18א אחרי חזרה מהמרתף.xlsx', sheet='Norton')
after = after[-(1:6),]

before$Norton = as.integer(before[['...7']])
after$Norton = as.integer(after[['...7']])

combined <- data.frame(Before = before$Norton, After = after$Norton)
```

### Before
```{r}
summary(before$Norton)

```
### after
```{r}
summary(after$Norton)

```

### P value is larger than 0.05, groups are **not** statistically different
```{r}

# 4. Statistical Tests
# Example: t-test for a continuous variable 'variable_of_interest'
t_test_result <- t.test(before$Norton, after$Norton)
print(t_test_result)
```


```{r}
# Scatter plot
plot(combined$Before, combined$After, xlab = "Before", ylab = "After", main = "Scatter plot of Norton values Before and After")
abline(0, 1, col = "red")  # Add a diagonal line for comparison

# Box plot
boxplot(combined, col = c("blue", "green"), names = c("Before", "After"), main = "Box plot of Before and After", xlab = "Group")

# Bar plot
mean_before <- mean(combined$Before)
mean_after <- mean(combined$After)
sd_before <- sd(combined$Before)
sd_after <- sd(combined$After)

# Create bar plot
means <- c(mean_before, mean_after)
stds <- c(sd_before, sd_after)
barplot(means, names.arg = c("Before", "After"), ylab = "Measurement", main = "Bar plot of Norton Means with Std Deviations", col = "blue", ylim = c(0, max(means) + max(stds) + 5))
arrows(x0 = c(0.7, 1.9), y0 = means - stds, y1 = means + stds, angle = 90, code = 3, length = 0.1)

```

# Morse 18
```{r morse}
before = read_excel('מורס 18 לפני ירידה למרתף .xlsx', sheet='Morse')
before = before[27,]
before <- unlist(before[grep("^\\d+$", before)])
before <- as.integer(before)

after = read_excel('מורס 18 אחרי חזרה לשגרה .xlsx', sheet='Morse')
after = after[27,]
after <- unlist(after[grep("^\\d+$", after)])
after <- as.integer(after)

combined <- data.frame(Before = before, After = after)
```

### Before
```{r}
summary(before)

```
### after
```{r}
summary(after)

```
### P value is larger than 0.05, groups are **not** statistically different

```{r}

# 4. Statistical Tests
# Example: t-test for a continuous variable 'variable_of_interest'
t_test_result <- t.test(before, after)
print(t_test_result)
```


```{r}
# Scatter plot
plot(combined$Before, combined$After, xlab = "Before", ylab = "After", main = "Scatter plot of Norton values Before and After")
abline(0, 1, col = "red")  # Add a diagonal line for comparison

# Box plot
boxplot(combined, col = c("blue", "green"), names = c("Before", "After"), main = "Box plot of Before and After", xlab = "Group")

# Bar plot
mean_before <- mean(combined$Before)
mean_after <- mean(combined$After)
sd_before <- sd(combined$Before)
sd_after <- sd(combined$After)

# Create bar plot
means <- c(mean_before, mean_after)
stds <- c(sd_before, sd_after)
barplot(means, names.arg = c("Before", "After"), ylab = "Measurement", main = "Bar plot of Norton Means with Std Deviations", col = "blue", ylim = c(0, max(means) + max(stds) + 5))
arrows(x0 = c(0.7, 1.9), y0 = means - stds, y1 = means + stds, angle = 90, code = 3, length = 0.1)

```

# Morse 18א
```{r}
before = read_excel('מורס 18א לפני ירידה למרתף .xlsx', sheet='Morse')
before = before[27,]
before <- unlist(before[grep("^\\d+$", before)])
before <- as.integer(before)

after = read_excel('מורס 18א אחרי חזרה לשגרה .xlsx', sheet='Morse')
after = after[27,]
after <- unlist(after[grep("^\\d+$", after)])
after <- as.integer(after)

combined <- data.frame(Before = before, After = after)
```

### Before
```{r}
summary(before)

```
### after
```{r}
summary(after)

```
### P value is larger than 0.05, groups are **not** statistically different

```{r}

# 4. Statistical Tests
# Example: t-test for a continuous variable 'variable_of_interest'
t_test_result <- t.test(before, after)
print(t_test_result)
```

```{r}
# Scatter plot
plot(combined$Before, combined$After, xlab = "Before", ylab = "After", main = "Scatter plot of Norton values Before and After")
abline(0, 1, col = "red")  # Add a diagonal line for comparison

# Box plot
boxplot(combined, col = c("blue", "green"), names = c("Before", "After"), main = "Box plot of Before and After", xlab = "Group")

# Bar plot
mean_before <- mean(combined$Before)
mean_after <- mean(combined$After)
sd_before <- sd(combined$Before)
sd_after <- sd(combined$After)

# Create bar plot
means <- c(mean_before, mean_after)
stds <- c(sd_before, sd_after)
barplot(means, names.arg = c("Before", "After"), ylab = "Measurement", main = "Bar plot of Norton Means with Std Deviations", col = "blue", ylim = c(0, max(means) + max(stds) + 5))
arrows(x0 = c(0.7, 1.9), y0 = means - stds, y1 = means + stds, angle = 90, code = 3, length = 0.1)

```

# Bartel 18
```{r bartel}
before = read_excel('ברטל 18 לפני ירידה לקומת המרתף .xlsx')
after = read_excel('ברטל 18 אחרי חזרה לשגרה .xlsx')


combined <- data.frame(Before = before$`ציון ברטל`, After = after$`ציון ברטל`)
```

### Before
```{r}
summary(before$`ציון ברטל`)

```
### after
```{r}
summary(after$`ציון ברטל`)

```
### P value is larger than 0.05, groups are **not** statistically different

```{r}

# 4. Statistical Tests
# Example: t-test for a continuous variable 'variable_of_interest'
t_test_result <- t.test(before, after)
print(t_test_result)
```


```{r}
# Scatter plot
plot(combined$Before, combined$After, xlab = "Before", ylab = "After", main = "Scatter plot of Bartel values Before and After")
abline(0, 1, col = "red")  # Add a diagonal line for comparison

# Box plot
boxplot(combined, col = c("blue", "green"), names = c("Before", "After"), main = "Box plot of Before and After", xlab = "Group")

# Bar plot
mean_before <- mean(combined$Before)
mean_after <- mean(combined$After)
sd_before <- sd(combined$Before)
sd_after <- sd(combined$After)

# Create bar plot
means <- c(mean_before, mean_after)
stds <- c(sd_before, sd_after)
barplot(means, names.arg = c("Before", "After"), ylab = "Measurement", main = "Bar plot of Bartel Means with Std Deviations", col = "blue", ylim = c(0, max(means) + max(stds) + 5))
arrows(x0 = c(0.7, 1.9), y0 = means - stds, y1 = means + stds, angle = 90, code = 3, length = 0.1)

```

# Bartel 18א
```{r}
before = read_excel('ברטל 18א לפני ירידה למרתף -.xlsx', sheet='manual inputs')
before = before[-(1:6),]
before$...12 <- as.integer(before$...12)


after = read_excel('ברטל 18א אחרי חזרה לשגרה.xlsx', sheet='manual inputs')
after = after[-(1:6),]
after$...12 <- as.integer(after$...12)



combined <- data.frame(Before = before$...12, After = after$...12)
```

### Before
```{r}
summary(before$...12)

```
### After 

```{r}
summary(after$...12)

```
### P value is larger than 0.05, groups are **not** statistically different

```{r}
# 4. Statistical Tests
# Example: t-test for a continuous variable 'variable_of_interest'
t_test_result <- t.test(before$...12, after$...12)
print(t_test_result)
```


```{r}
# Scatter plot
plot(combined$Before, combined$After, xlab = "Before", ylab = "After", main = "Scatter plot of Bartel values Before and After")
abline(0, 1, col = "red")  # Add a diagonal line for comparison

# Box plot
boxplot(combined, col = c("blue", "green"), names = c("Before", "After"), main = "Box plot of Before and After", xlab = "Group")

# Bar plot
mean_before <- mean(combined$Before)
mean_after <- mean(combined$After)
sd_before <- sd(combined$Before)
sd_after <- sd(combined$After)

# Create bar plot
means <- c(mean_before, mean_after)
stds <- c(sd_before, sd_after)
barplot(means, names.arg = c("Before", "After"), ylab = "Measurement", main = "Bar plot of Bartel Means with Std Deviations", col = "blue", ylim = c(0, max(means) + max(stds) + 5))
arrows(x0 = c(0.7, 1.9), y0 = means - stds, y1 = means + stds, angle = 90, code = 3, length = 0.1)

```

